Software Citation Principles

### 2016-06-23 sc-principles/software-citation-principles.tex
italicized unique identification recommendation

The Unique Identification principle~(\ref{principle:uid}) calls for ``a method for identification that is machine actionable, globally unique, interoperable, and recognized by a community.''
What this means for data is discussed in detail in the ``Unique Identification'' section of a report by the FORCE11 Data Citation Implementation Group (DCIG)~\cite{10.7717/peerj-cs.1}, which calls for ``unique identification in a manner that is machine-resolvable on the Web and demonstrates a long-term commitment to persistence.''
This report also lists examples of identifiers that match these criteria including DOIs, PURLs, Handles, ARKS, and NBNs.
For software, we recommend the use of DOIs as the unique identifier due to their common usage and acceptance, particularly as they are the standard for other digital products such as publications.

>>>>

The Unique Identification principle~(\ref{principle:uid}) calls for ``a method for identification that is machine actionable, globally unique, interoperable, and recognized by a community.''
What this means for data is discussed in detail in the ``Unique Identification'' section of a report by the FORCE11 Data Citation Implementation Group (DCIG)~\cite{10.7717/peerj-cs.1}, which calls for ``unique identification in a manner that is machine-resolvable on the Web and demonstrates a long-term commitment to persistence.''
This report also lists examples of identifiers that match these criteria including DOIs, PURLs, Handles, ARKS, and NBNs.
For software, \textit{we recommend the use of DOIs as the unique identifier due to their common usage and acceptance, particularly as they are the standard for other digital products such as publications.}
